LCS Tool — An Algorithmic Introduction to Lagrangian Coherent Structures

### 2014-02-19 main.tex
Use \equiv symbol for definitions
Rename double gyre section and remove table of contents

\tableofcontents

@@

The fluid flows considered are defined in two dimensions by a velocity field:
\begin{align*}
\dot{\boldsymbol x} = \boldsymbol v(\boldsymbol x,t), && \boldsymbol x \in U \subset \reals^2, && t \in [t_-,t_+].
\end{align*}
Integration yields the flow map, defined between an initial time $t_0$ and a final time $t$ within $[t_-,t_+]$:
\[
F_{t_0}^t(\boldsymbol x_0) := \boldsymbol x(t,t_0,\boldsymbol x_0).
\]
The time interval used to detect LCSs is arbitrary; it can be the complete interval for which the flow is defined, or data is available, or it can be a sub-interval.

@@

\subsection{The double gyre}
The double gyre is a model for a time-dependent two gyre system observed in geophysical flows \parencite{shadden05:_defin_lagran_lyapun}. It consists of two counter rotating sinusoidal vortices with a harmonically oscillating line in-between. The velocity equations are:
\begin{equation}
\begin{split}
\dot x = -\pi A \sin[\pi f(x,t)] \cos(\pi y)\\
\dot y = \pi A \cos[\pi f(x,t)] \sin(\pi y) \frac{\partial f(x,t)}{\partial x}\\
f(x,t) = \epsilon \sin(\omega t) x^2 + [1 - 2 \epsilon \sin(\omega t)] x.
\end{split}
\label{eq:double gyre derivative equations}
\end{equation}
The MATLAB function corresponding to these equations is given in Listing~\ref{l:double gyre derivative} and shows how to specify a derivative function that supports vector form integration.

>>>>

@@

The fluid flows considered are defined in two dimensions by a velocity field:
\begin{align*}
\dot{\boldsymbol x} = \boldsymbol v(\boldsymbol x,t), && \boldsymbol x \in U \subset \reals^2, && t \in [t_-,t_+].
\end{align*}
Integration yields the flow map, defined between an initial time $t_0$ and a final time $t$ within $[t_-,t_+]$:
\[
F_{t_0}^t(\boldsymbol x_0) \equiv \boldsymbol x(t,t_0,\boldsymbol x_0).
\]
The time interval used to detect LCSs is arbitrary; it can be the complete interval for which the flow is defined, or data is available, or it can be a sub-interval.

@@

\subsection{Double gyre}
The double gyre is a model for a time-dependent two gyre system observed in geophysical flows \parencite{shadden05:_defin_lagran_lyapun}. It consists of two counter rotating sinusoidal vortices with a harmonically oscillating line in-between. The velocity equations are:
\begin{equation}
\begin{split}
\dot x = -\pi A \sin[\pi f(x,t)] \cos(\pi y)\\
\dot y = \pi A \cos[\pi f(x,t)] \sin(\pi y) \frac{\partial f(x,t)}{\partial x}\\
f(x,t) = \epsilon \sin(\omega t) x^2 + [1 - 2 \epsilon \sin(\omega t)] x.
\end{split}
\label{eq:double gyre derivative equations}
\end{equation}
The MATLAB function corresponding to these equations is given in Listing~\ref{l:double gyre derivative} and shows how to specify a derivative function that supports vector form integration.
